---
title: "Data_exploration"
output: html_notebook
---
# Libraries
```{r}
library(faraway)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(reshape2)
```


# pulling in DFs and Merging
```{r}
#red wines
Red_wine <- read.csv("wineQualityReds.csv", header=TRUE, sep = ",")
Red_wine$Type <- 'Red'

#white wines
White_wine <- read.csv("wineQualityWhites.csv", header=TRUE, sep = ",")
White_wine$Type <- 'White'

## consolidated
Data <- rbind(Red_wine,White_wine)
drops <- c("X")
Data <- Data[ , !(names(Data) %in% drops)]
Data

##create final DF
# write.csv(Data,"/Users/colinobrien/Desktop/repo/stats_6021/Stats_project_group_6/Data.csv", row.names = FALSE)
# write.csv(Data,"/Users/colinobrien/Desktop/repo/stats_6021/Stats_project_group_6/Data", row.names = FALSE)
## both the Data and Data csv are the same. I know people prefer one format vs the other so I made both

```


```{r}
Data_Final <- Data %>%
  mutate(cat_quality = 
           case_when(quality<6 ~ 'Low',
                     quality>=6 ~ 'High')
         )
Data_Final

write.csv(Data_Final,"/Users/colinobrien/Desktop/repo/stats_6021/Stats_project_group_6/Data.csv", row.names = FALSE)


```

# Creating Training and testing Data

```{r}
set.seed(90210)
sample<-sample.int(nrow(Data), floor(.80*nrow(Data)), replace = F)
train<-Data[sample, ] ##training data
test<-Data[-sample, ] ##test data


```



# Some General Data Explortation
```{r}

drops_type <- c("Type")
No_Type_train <- train[ , !(names(train) %in% drops_type)]
# No_Type

pairs(No_Type_train, lower.panel = NULL)
```
```{r}
cor_train_no_type <- cor(No_Type_train)
cor_train_no_type
```
```{r}
T_F_cor <- abs(cor_train_no_type)>.7
T_F_cor
```
total.sulfur.dioxide and free.sulfur.dioxide are pretty highly correlated (positive). Neither have high VIF scores below though


```{r}
## create melted
melted_cor_train_no_type <- melt(cor_train_no_type)
head(melted_cor_train_no_type)

##create heat map
ggplot(data = melted_cor_train_no_type, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+
  coord_fixed()
```
alc/densit and free.sulfur.dioxide/total.sulfur.dioxide have the strongest corelations

#### http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization  Source used to help create heatmap


```{r}
vif(No_Type_train)
```

Within the training, Density, residual.sugar have a high VIF score. fixed.acidity and alcohol are borderline

## cor for red and for white


```{r}
# Red_wine
# White_wine
#### go back and make this TRAINING !!!!!!!!!!
drops_type <- c("Type")
No_Type_white <- White_wine[ , !(names(White_wine) %in% drops_type)]
drops <- c("X")
No_Type_white <- No_Type_white[ , !(names(No_Type_white) %in% drops)]
##creating cor
No_Type_white_cor <- cor(No_Type_white)
#melt
melted_white <- melt(No_Type_white_cor)
melted_white

#create heat map
ggplot(data = melted_white, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+
  coord_fixed()+
  labs(title = 'White')
#############
#red
#############
drops_type <- c("Type")
No_Type_Red <- Red_wine[ , !(names(Red_wine) %in% drops_type)]
drops <- c("X")
No_Type_Red <- No_Type_Red[ , !(names(No_Type_Red) %in% drops)]
##creating cor
No_Type_Red_cor <- cor(No_Type_Red)
#melt
melted_Red <- melt(No_Type_Red_cor)
melted_Red

#create heat map
ggplot(data = melted_Red, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+
  coord_fixed()+
  labs(title = 'Red')


### finding the dif

the_dif <- No_Type_Red_cor-No_Type_white_cor
the_dif
```


```{r}
### finding the dif

the_dif <- No_Type_Red_cor-No_Type_white_cor
the_dif
```
```{r}
melted_dif <- melt(the_dif)
#create heat map
ggplot(data = melted_dif, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-.5,.5), space = "Lab", name="Pearson\nCorrelation") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+
  coord_fixed()+
  labs(title = 'Red')
```


```{r}
ggplot(data = Data) + 
  geom_bar(mapping = aes(x = quality, fill = Type))
```


#