---
title: "R Notebook"
output: html_notebook
---

```{r}
library(faraway)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(leaps)
```

```{r}
Data_Final <- read.csv("Data_Final.csv", header=TRUE, sep = ",", stringsAsFactors=TRUE)
Data_Final <- subset(Data_Final, select = -c(quality))
Data_Final
Data_Final$cat_quality <- as.integer(Data_Final$cat_quality == "High")
```
```{r}
set.seed(90210)
sample<-sample.int(nrow(Data_Final), floor(.80*nrow(Data_Final)), replace = F)
train<-Data_Final[sample, ] ##training data
test<-Data_Final[-sample, ] ##test data

train
```
### changing factors



```{r}
## Convert to 0 and 1 for readability
# train$cat_quality <- as.integer(train$cat_quality == "High")
# test$cat_quality <- as.integer(test$cat_quality == "High")
# train
```



```{r}
#training
# train$cat_quality<-factor(train$cat_quality)
# levels(train$cat_quality) <- c(0,1)
# levels(train$cat_quality)
# 
# 
# train$Type<-factor(train$Type)
# levels(train$Type) <- c(0,1)
# levels(train$Type)
# 
# train
# 
# 
# #test
# test$cat_quality<-factor(test$cat_quality)
# levels(test$cat_quality) <- c(0,1)
# levels(test$cat_quality)
# 
# 
# test$Type<-factor(test$Type)
# levels(test$Type) <- c(0,1)
# levels(test$Type)
# 
# test
```


### added the press formula
```{r}
get_press <- function(model) {
  sum(((model$residuals)/ (1- (lm.influence(model)$hat)))^2)
}
```




#running regression 
## first go

```{r}
full<-glm(cat_quality~., family=binomial, data=train)
summary(full)
```


```{r}
## removed all insignificant
reduced_1<-glm(formula = cat_quality~., family=binomial, data=train)
summary(reduced_1)
```


```{r}
##evaluating model
Reduced1_AIC_train <- reduced_1$aic

##predicted quality for test data based on training data
preds<-predict(reduced_1,newdata=test, type="response")

reduced_1_error <- table(test$cat_quality, preds>0.5)

reduced_1_error

evulation_summary <- data.frame(
  attempt = 'reduced_1',
  AIC = Reduced1_AIC_train,
  PRESS = get_press(reduced_1),
  'False positive' = round(reduced_1_error[3]/(reduced_1_error[1]+reduced_1_error[3]),3),
  'False negative' = round(reduced_1_error[2]/(reduced_1_error[2]+reduced_1_error[4]),3),
  'Error Rate' = round((reduced_1_error[2]+reduced_1_error[3])/(reduced_1_error[1]+reduced_1_error[2]+reduced_1_error[3]+reduced_1_error[4]),3)
)
evulation_summary
```

## Second go

```{r}
#this time looking at VIF scores from exploration
# drops_type <- c("Type","quality")
# Round_2_train <- train[ , !(names(train) %in% drops_type)]
# Round_2_train

# vif(Round_2_train)

```



```{r}

## take out alc (highly correlated with Density)
reduced_2<-glm(cat_quality~fixed.acidity+volatile.acidity+citric.acid+residual.sugar+total.sulfur.dioxide+density+chlorides+free.sulfur.dioxide+pH+sulphates+Type, family=binomial, data=train)
summary(reduced_2)
```
```{r}


## removed citric.acid and chlorides based on p values
reduced_2_2<-glm(cat_quality~fixed.acidity+volatile.acidity+residual.sugar+total.sulfur.dioxide+density+free.sulfur.dioxide+pH+sulphates+Type, family=binomial, data=train)
summary(reduced_2_2)
```

```{r}
##evaluating model
Reduced2_AIC_train <- reduced_2_2$aic

##predicted quality for test data based on training data
preds<-predict(reduced_2_2,newdata=test, type="response")

reduced_2_2_error <- table(test$cat_quality, preds>0.5)

evulation_summary_2 <- data.frame(
  attempt = 'reduced_2_2_error',
  AIC = Reduced2_AIC_train,
  PRESS = get_press(reduced_2_2),
  'False positive' = round(reduced_2_2_error[3]/(reduced_2_2_error[1]+reduced_2_2_error[3]),3),
  'False negative' = round(reduced_2_2_error[2]/(reduced_2_2_error[2]+reduced_2_2_error[4]),3),
  'Error Rate' = round((reduced_2_2_error[2]+reduced_2_2_error[3])/(reduced_2_2_error[1]+reduced_2_2_error[2]+reduced_2_2_error[3]+reduced_2_2_error[4]),3)
)

evulation_summary <- rbind(evulation_summary,evulation_summary_2)
evulation_summary
```
<!-- ## third go -->

<!-- this time I try all possible regressions  -->

<!-- ```{r} -->
<!-- ## https://rstudio-pubs-static.s3.amazonaws.com/2897_9220b21cfc0c43a396ff9abf122bb351.html -->
<!-- ``` -->


<!-- ```{r} -->
<!-- regsubsets.out <- -->
<!--     regsubsets(cat_quality~fixed.acidity+volatile.acidity+citric.acid+residual.sugar+total.sulfur.dioxide+density+chlorides+free.sulfur.dioxide+pH+sulphates+alcohol+Type, -->
<!--                data = train, -->
<!--                nbest = 1,       # 1 best model for each number of predictors -->
<!--                nvmax = NULL,    # NULL for no limit on number of variables -->
<!--                force.in = NULL, force.out = NULL, -->
<!--                method = "exhaustive") -->
<!-- regsubsets.out -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary.out <- summary(regsubsets.out) -->
<!-- as.data.frame(summary.out$outmat) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ## Adjusted R2 -->
<!-- plot(regsubsets.out, scale = "adjr2", main = "Adjusted R^2") -->
<!-- ``` -->
<!-- Based on this chart, the model with the lowest R^2 would have all  -->


<!-- ```{r} -->
<!-- reduced_3<-glm(cat_quality~fixed.acidity+volatile.acidity+citric.acid+residual.sugar+total.sulfur.dioxide+density+chlorides+free.sulfur.dioxide+pH+sulphates+alcohol+Type, family=binomial, data=train) -->
<!-- summary(reduced_3) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ##evaluating model -->
<!-- Reduced3_AIC_train <- reduced_3$aic -->

<!-- ##predicted quality for test data based on training data -->
<!-- preds<-predict(reduced_3,newdata=test, type="response") -->

<!-- reduced_3_error <- table(test$cat_quality, preds>0.5) -->

<!-- evulation_summary_3 <- data.frame( -->
<!--   attempt = 'reduced_3_error', -->
<!--   AIC = Reduced3_AIC_train, -->
<!--   PRESS = get_press(reduced_3), -->
<!--   'False positive' = round(reduced_3_error[3]/(reduced_3_error[1]+reduced_3_error[3]),3), -->
<!--   'False negative' = round(reduced_3_error[2]/(reduced_3_error[2]+reduced_3_error[4]),3), -->
<!--   'Error Rate' = round((reduced_3_error[2]+reduced_3_error[3])/(reduced_3_error[1]+reduced_3_error[2]+reduced_3_error[3]+reduced_3_error[4]),3) -->
<!-- ) -->

<!-- evulation_summary <- rbind(evulation_summary,evulation_summary_3) -->
<!-- evulation_summary -->
<!-- ``` -->


## go 4
Given the number of parameters, I used the best possible model method this time :-)

## https://rstudio-pubs-static.s3.amazonaws.com/2897_9220b21cfc0c43a396ff9abf122bb351.html

<!-- ```{r} -->
<!-- # ## Mallow Cp -->
<!-- # library(car) -->
<!-- # regsubsets.out_2 <- -->
<!-- #     regsubsets(quality~fixed.acidity+volatile.acidity+citric.acid+residual.sugar+total.sulfur.dioxide+density+chlorides+free.sulfur.dioxide+pH+sulphates+alcohol+Type, -->
<!-- #                data = train, -->
<!-- #                nbest = 1,       # 1 best model for each number of predictors -->
<!-- #                nvmax = NULL,    # NULL for no limit on number of variables -->
<!-- #                force.in = NULL, force.out = NULL, -->
<!-- #                method = "exhaustive") -->
<!-- # regsubsets.out_2 -->
<!-- #  -->
<!-- #  -->
<!-- # res.legend_2 <-subsets(regsubsets.out_2, statistic="cp", legend = FALSE, min.size = 8, main = "Mallow Cp") -->
<!-- # abline(a = 1, b = 1, lty = 2) -->
<!-- # res.legend_2 -->
<!-- ``` -->





```{r}
# install.packages("bestglm")
library(bestglm)
## Prepare data
train.for.best.logistic <- within(train, {
    quality <- NULL
    y <- cat_quality 
})

## Reorder variables
train.for.best.logistic <-
    train.for.best.logistic[, c("fixed.acidity","volatile.acidity","citric.acid","residual.sugar","total.sulfur.dioxide","density","chlorides","free.sulfur.dioxide",'pH','sulphates','alcohol','Type',"y")]

## Perform
res.best.logistic <-
    bestglm(Xy = train.for.best.logistic,
            family = binomial,          # binomial family for logistic
            IC = "AIC",                 # Information criteria for
            method = "exhaustive")
```


```{r}
res.best.logistic$BestModels
```

```{r}
summary(res.best.logistic$BestModel)
```

```{r}

reduced_4 <- res.best.logistic$BestModel
##evaluating model
Reduced4_AIC_train <- reduced_4$aic

##predicted quality for test data based on training data
preds<-predict(reduced_4,newdata=test, type="response")

reduced_4_error <- table(test$cat_quality, preds>0.5)

evulation_summary_4 <- data.frame(
  attempt = 'reduced_4_error',
  AIC = Reduced4_AIC_train,
  PRESS = get_press(reduced_4),
  'False positive' = round(reduced_4_error[3]/(reduced_4_error[1]+reduced_4_error[3]),3),
  'False negative' = round(reduced_4_error[2]/(reduced_4_error[2]+reduced_4_error[4]),3),
  'Error Rate' = round((reduced_4_error[2]+reduced_4_error[3])/(reduced_4_error[1]+reduced_4_error[2]+reduced_4_error[3]+reduced_4_error[4]),3)
)

evulation_summary <- rbind(evulation_summary,evulation_summary_4)
evulation_summary
```

## go 5

here I was curious as to what would be variables that anyone could quickly access (not needing to go to a lab) via a wine label/tasting the wine. 



```{r}
easy_peasy <- c('residual.sugar','chlorides','Type','density', 'pH', 'alcohol')
```

```{r}
reduced_5<-glm(cat_quality~residual.sugar+chlorides+Type+density+pH+alcohol, family=binomial, data=train)
summary(reduced_5)
```
Since Density is correlated with alc and acl has low p, remove Density 

```{r}
reduced_5_2<-glm(cat_quality~residual.sugar+chlorides+Type+pH+alcohol, family=binomial, data=train)
summary(reduced_5_2)
```

Due to high P, removing pH 

```{r}
reduced_5_3<-glm(cat_quality~residual.sugar+chlorides+Type+alcohol, family=binomial, data=train)
summary(reduced_5_3)
```

```{r}

Reduced5_AIC_train <- reduced_5_3$aic

##predicted quality for test data based on training data
preds<-predict(reduced_5_3,newdata=test, type="response")

reduced_5_error <- table(test$cat_quality, preds>0.5)

evulation_summary_5 <- data.frame(
  attempt = 'reduced_5_error',
  AIC = Reduced5_AIC_train,
  PRESS = get_press(reduced_5_3),
  'False positive' = round(reduced_5_error[3]/(reduced_5_error[1]+reduced_5_error[3]),3),
  'False negative' = round(reduced_5_error[2]/(reduced_5_error[2]+reduced_5_error[4]),3),
  'Error Rate' = round((reduced_5_error[2]+reduced_5_error[3])/(reduced_5_error[1]+reduced_5_error[2]+reduced_5_error[3]+reduced_5_error[4]),3)
)


evulation_summary <- rbind(evulation_summary,evulation_summary_5)
evulation_summary
```



```{r}
result <- glm(formula = cat_quality ~ alcohol + volatile.acidity + density + 
    sulphates + residual.sugar + Type + total.sulfur.dioxide + 
    free.sulfur.dioxide + pH + citric.acid + fixed.acidity, family = "binomial", 
    data = train)
preds <- predict(result,newdata=test, type="response")
table(test$cat_quality, preds>0.5)
```


